---
fig_height: 3
fig_width: 5
output:
  html_document:
    theme: yeti
params:
  hourly_rate: 15
  client_hourly_rate: 30
  new_hourly_rate: 20
  new_client_hourly_rate: 40
  start_date: '2016-01-01'
  end_date: '2019-02-24'
  fetch_new: TRUE
---

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE, cache = F}
# No scientific notation
options(scipen=999)
library(Quandl)
library(knitr)
library(tidyverse)
library(gsheet)
library(DT)
library(tidyr)
library(ggthemes)
library(yaml)

# Basic knitr options
opts_chunk$set(comment = NA, 
               echo = FALSE, 
               warning = FALSE, 
               message = FALSE, 
               error = TRUE, 
               cache = FALSE)
```

```{r}
# Specify paramaters
for (i in 1:length(params)){
  assign(names(params)[i],
         params[[i]],
         env = .GlobalEnv)
}

creation_date <- as.Date(Sys.Date())
```

```{r}
file_name <- paste0(creation_date, '.RData')
has <- function(x){
  out <- FALSE
  if(!is.null(x)){
    if(x != ''){
      out <- TRUE
    }
  }
  return(out)
}

has_start_date <- has(start_date)
has_end_date <- has(end_date)
if(!has_start_date){
  start_date <- as.Date('2015-01-01')
} else{
  start_date <- as.Date(start_date)
}
if(!has_end_date){
  end_date <- as.Date(Sys.Date())
} else {
  end_date <- as.Date(end_date)
}

# if(file_name %in% dir('backups') & !fetch_new){
#   load(paste0('backups/', file_name))
# } else {
  # Get accounting data
  expenses <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1RABWgak2e2i2blu1tLUmbNHagJGrh7MPbivuXB2TCDM/edit#gid=0')
  income <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1RABWgak2e2i2blu1tLUmbNHagJGrh7MPbivuXB2TCDM/edit#gid=684913063')
  hours <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1RABWgak2e2i2blu1tLUmbNHagJGrh7MPbivuXB2TCDM/edit#gid=565858805')
  hours2019 <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1RABWgak2e2i2blu1tLUmbNHagJGrh7MPbivuXB2TCDM/edit#gid=335157130')
  hours <- bind_rows(hours, hours2019)
  wages_paid <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1RABWgak2e2i2blu1tLUmbNHagJGrh7MPbivuXB2TCDM/edit#gid=1319225983')
#   save(expenses, income, hours,
#        file = paste0('backups/', file_name))
# }
expenses$date <- as.Date(expenses$date, format = '%m/%d/%Y')
hours$date <- as.Date(hours$date, format = '%m/%d/%Y')
income$date <- as.Date(income$date, format = '%m/%d/%Y')
wages_paid$date <- as.Date(wages_paid$date, format = '%m/%d/%Y')
# Make all data frames
expenses <- data.frame(expenses)
hours <- data.frame(hours)
income <- data.frame(income)
wages_paid <- data.frame(wages_paid)

date_restrict <- function(x){
  x %>% filter(date >= start_date, date <= end_date)
}
expenses <- date_restrict(expenses)
hours <- date_restrict(hours)
income <- date_restrict(income)
wages_paid <- date_restrict(wages_paid)

# Get currency data
credentials <- yaml.load_file('credentials.yaml')
currency <- Quandl("BOE/XUDLCDD", 
                   api_key=credentials$quandl_api)
eur_currency <- Quandl("ECB/EURUSD",
                       api_key = credentials$quandl_api)
names(eur_currency) <- c('date', 'eur_to_usd')
eur_currency$usd_to_eur <- 1 / eur_currency$eur_to_usd
eur_currency$eur_to_usd <- NULL
names(currency) <- c('date', 'usd_to_cad')
# Combine
currency <- left_join(currency, eur_currency)
currency <- currency %>% filter(!is.na(usd_to_cad),
                                !is.na(usd_to_eur))

# Expand out to sys date if needed
currency <- left_join(data_frame(date = seq(min(currency$date),
                                 Sys.Date(),
                                 by = 1)),
                      currency) 
currency <- currency %>% arrange(date) %>%
  tidyr::fill(usd_to_cad, usd_to_eur, .direction = 'down')
# Create usd columns
expenses <-
  left_join(expenses, currency,
            by = 'date') %>%
  mutate(usd = ifelse(currency == 'CAD',
                      amount / usd_to_cad,
                      ifelse(currency == 'EUR',
                             amount / usd_to_eur,
                             amount)))
income <- left_join(income, currency,
                    by = 'date') %>%
  mutate(usd = ifelse(currency == 'CAD',
                      amount / usd_to_cad,
                      ifelse(currency == 'EUR',
                             amount / usd_to_eur,
                             amount)))
wages_paid <- left_join(wages_paid, currency,
                         by = 'date') %>%
  mutate(usd = ifelse(currency == 'CAD',
                      amount / usd_to_cad,
                      ifelse(currency == 'EUR',
                             amount / usd_to_eur,
                             amount)))

x = hours %>%
  mutate(status = ifelse(high_priority, 'External', 'Internal')) %>%
  group_by(status, name) %>%
  summarise(hours = sum(total_hours)) %>%
  ungroup
# ggplot(data = x,
#        aes(x = name,
#            y = hours,
#            group = status,
#            fill = status)) +
#   geom_bar(stat = 'identity',
#            position = 'dodge') +
#   databrew::theme_databrew()
```

```{r, results = 'hide'}
# Get amount in Canadian bank
source('accounting_get_bank_data.R')
bank <- get_bank_money()

# Convert to usd
bank <- left_join(bank, currency)
bank$usd <- ifelse(bank$currency == 'USD',
                   bank$value,
                   bank$value * (1/bank$usd_to_cad))
bank$usd_to_cad <- NULL
detailed_bank <- bank
# Combine the two banks together and sum
bank <- bank %>%
  group_by(date) %>%
  summarise(usd = sum(usd)) %>%
  ungroup

bank <- bank %>% arrange(date)
# {.tabset .tabset-fade .tabset-pills}
```


# Databrew internal accounting 

## REPORT PERIOD:  

`r params$start_date` through `r params$end_date`. All values (including yearly totals). refer only to this period



```{r, results = 'asis'}
# ## Non-wage expenses over time
# 
# The below shows the cumulative total of expenses incurred over time (hardware purchase, domains, licensing, server hosting, laptops, etc.)
# Get all expenditures
x <- expenses %>%
  filter(date >= start_date, date <= end_date) %>%
  filter(!is.na(reimbursed)) %>%
  filter(!reimbursed) %>%
  dplyr::select(date, usd, item) %>%
  # mutate(usd = -1 * usd) %>%
  # bind_rows(
  #   income %>%
  #     dplyr::select(date, usd)
  # ) %>%
  arrange(date) %>%
  mutate(balance = cumsum(usd))
x <- left_join(data_frame(date = seq(min(x$date),
                                     Sys.Date(),
                                     by = 1)),
               x,
               by = 'date') %>%
  arrange(date)
x <- x %>%
  tidyr::fill(balance, .direction = 'down')

# ggplot(data = x,
#        aes(x = date,
#            y = balance)) +
#   geom_step(alpha = 0.7) +
#   geom_hline(yintercept = 0, col = 'black',
#              lty = 3, alpha = 0.6) +
#   theme_fivethirtyeight() +
#   labs(x = 'Date',
#        y = 'Balance',
#        title = paste0('All expenses: ', round(dplyr::last(x$balance)), ' USD'),
#        subtitle = '(Ignores hours worked and income)')

# DT::datatable(x %>% filter(!is.na(usd)) %>%
#                 mutate(usd = round(usd, digits = 2),
#                        balance = round(balance, digits = 2)))
```


```{r}
# Define date of changing to increased wages
change_date <- as.Date('2019-07-01')

# Add year columns
hours$year <- as.numeric(format(hours$date, '%Y'))
expenses$year <- as.numeric(format(expenses$date, '%Y'))
income$year <- as.numeric(format(income$date, '%Y'))
wages_paid$year <- as.numeric(format(wages_paid$date, '%Y'))

# Add a pre incorporation/ post incorporation column
hours$llc <- ifelse(hours$date >= '2019-02-25', 'After Feb 25 2019','Before Feb 25 2019')
expenses$llc <- ifelse(expenses$date >= '2019-02-25', 'After Feb 25 2019','Before Feb 25 2019')
income$llc <- ifelse(income$date >= '2019-02-25', 'After Feb 25 2019','Before Feb 25 2019')
wages_paid$llc <- ifelse(wages_paid$date >= '2019-02-25', 'After Feb 25 2019','Before Feb 25 2019')

# Filter
hours <- hours %>% filter(date >= start_date, date <= end_date)
expenses <- expenses %>% filter(date >= start_date, date <= end_date)
income <- income %>% filter(date >= start_date, date <= end_date)
wages_paid <- wages_paid %>% filter(date >= start_date, date <= end_date)
# Overwrite names (absorbing spouses)
hours <- hours %>% mutate(name = ifelse(name == 'Xing', 'Ben',
                       ifelse(name == 'Coloma',
                              'Joe',
                              name))) 
expenses <- expenses %>% mutate(payment_by = ifelse(payment_by == 'Xing', 'Ben',
                       ifelse(payment_by == 'Coloma',
                              'Joe',
                              payment_by))) 
income <- income %>% mutate(paid_to = ifelse(paid_to == 'Xing', 'Ben',
                       ifelse(paid_to == 'Coloma',
                              'Joe',
                              paid_to))) 
wages_paid <- wages_paid %>% mutate(name = ifelse(name == 'Xing', 'Ben',
                       ifelse(name == 'Coloma',
                              'Joe',
                              name))) 
names_df <- data.frame(name = c(sort(unique(hours$name))))


# Get all hours worked which have not yet been paid
hours_money <-
  hours %>%
  # filter(!paid_to_worker) %>%
  group_by(name) %>%
  summarise(total_hours_old = sum(total_hours[date < change_date]),
            total_hours_new = sum(total_hours[date >= change_date]))
hours_money_client <-
  hours %>%
  filter(billable_to_client) %>%
  group_by(name) %>%
  summarise(total_hours_client_old = sum(total_hours[date < change_date]),
            total_hours_client_new = sum(total_hours[date >= change_date]))
hours_money <- left_join(x = hours_money,
                         y = hours_money_client,
                         by = 'name')
hours_money <- left_join(names_df, hours_money) %>% 
  mutate(total_hours_old = ifelse(is.na(total_hours_old), 0, total_hours_old),
         total_hours_new = ifelse(is.na(total_hours_new), 0, total_hours_new),
         total_hours_client_old = ifelse(is.na(total_hours_client_old), 0, total_hours_client_old),
         total_hours_client_new = ifelse(is.na(total_hours_client_new), 0, total_hours_client_new))
hours_money <- hours_money %>%
  mutate(total_hours = total_hours_old + total_hours_new,
         total_hours_client = total_hours_client_old + total_hours_client_new) %>%
  mutate(percent_client = total_hours_client / total_hours * 100) %>%
  mutate(total_hours_internal = total_hours - total_hours_client) %>%
  mutate(total_hours_internal_new = total_hours_new - total_hours_client_new,
         total_hours_internal_old = total_hours_old - total_hours_client_old)

# Get all hours worked which have not yet been paid BY YEAR
hours_money_year <-
  hours %>%
  # filter(!paid_to_worker) %>%
  group_by(name, year) %>%
  summarise(total_hours_old = sum(total_hours[date < change_date]),
            total_hours_new = sum(total_hours[date >= change_date]))
hours_money_client_year <-
  hours %>%
  filter(billable_to_client) %>%
  group_by(name, year) %>%
  summarise(total_hours_client_old = sum(total_hours[date < change_date]),
            total_hours_client_new = sum(total_hours[date >= change_date]))
hours_money_year <- left_join(x = hours_money_year,
                         y = hours_money_client_year,
                         by = c('name', 'year'))
left <- expand.grid(year = sort(unique(hours_money_year$year)),
                    name = sort(unique(names_df$name)))
hours_money_year <- left_join(left, hours_money_year) %>% 
  mutate(total_hours_old = ifelse(is.na(total_hours_old), 0, total_hours_old),
         total_hours_new = ifelse(is.na(total_hours_new), 0, total_hours_new),
         total_hours_client_old = ifelse(is.na(total_hours_client_old), 0, total_hours_client_old),
         total_hours_client_new = ifelse(is.na(total_hours_client_new), 0, total_hours_client_new))
hours_money_year <- hours_money_year %>%
  mutate(total_hours = total_hours_old + total_hours_new,
         total_hours_client = total_hours_client_old + total_hours_client_new) %>%
  mutate(percent_client = total_hours_client / total_hours * 100) %>%
  mutate(total_hours_internal = total_hours - total_hours_client) %>%
  mutate(total_hours_internal_new = total_hours_new - total_hours_client_new,
         total_hours_internal_old = total_hours_old - total_hours_client_old)

# Get all hours worked which have not yet been paid whether before or after incorporation as LLC
hours_money_llc <-
  hours %>%
  # filter(!paid_to_worker) %>%
  group_by(name, llc) %>%
  summarise(total_hours_old = sum(total_hours[date < change_date]),
            total_hours_new = sum(total_hours[date >= change_date]))
hours_money_client_llc <-
  hours %>%
  filter(billable_to_client) %>%
  group_by(name, llc) %>%
  summarise(total_hours_client_old = sum(total_hours[date < change_date]),
            total_hours_client_new = sum(total_hours[date >= change_date]))
hours_money_llc <- left_join(x = hours_money_llc,
                         y = hours_money_client_llc,
                         by = c('name', 'llc'))
left_llc <- expand.grid(llc = sort(unique(hours_money_llc$llc)),
                    name = sort(unique(names_df$name)))
hours_money_llc <- left_join(left_llc, hours_money_llc) %>% 
  mutate(total_hours_old = ifelse(is.na(total_hours_old), 0, total_hours_old),
         total_hours_new = ifelse(is.na(total_hours_new), 0, total_hours_new),
         total_hours_client_old = ifelse(is.na(total_hours_client_old), 0, total_hours_client_old),
         total_hours_client_new = ifelse(is.na(total_hours_client_new), 0, total_hours_client_new))
hours_money_llc <- hours_money_llc %>%
  mutate(total_hours = total_hours_old + total_hours_new,
         total_hours_client = total_hours_client_old + total_hours_client_new) %>%
  mutate(percent_client = total_hours_client / total_hours * 100) %>%
  mutate(total_hours_internal = total_hours - total_hours_client) %>%
  mutate(total_hours_internal_new = total_hours_new - total_hours_client_new,
         total_hours_internal_old = total_hours_old - total_hours_client_old)



# Get all expenditures by any person which have not yet been reimbursed
ex_money <- expenses %>%
  filter(!reimbursed) %>%
  group_by(name = payment_by) %>%
  summarise(total_ex = sum(usd))
ex_money <- left_join(names_df, ex_money) %>% mutate(total_ex = ifelse(is.na(total_ex), 0, total_ex))

# Get all expenditures by any person which have not yet been reimbursed BY YEAR
ex_money_year <- expenses %>%
  filter(!reimbursed) %>%
  group_by(name = payment_by, year) %>%
  summarise(total_ex = sum(usd))
ex_money_year <- left_join(left, ex_money_year) %>% mutate(total_ex = ifelse(is.na(total_ex), 0, total_ex))

# Get all expenditures by any person which have not yet been reimbursed pre/post LLC
ex_money_llc <- expenses %>%
  filter(!reimbursed) %>%
  group_by(name = payment_by, llc) %>%
  summarise(total_ex = sum(usd))
ex_money_llc <- left_join(left_llc, ex_money_llc) %>% mutate(total_ex = ifelse(is.na(total_ex), 0, total_ex))

# Get total income paid to any one person which should have been collective
in_money <- income %>%
  group_by(name = paid_to) %>%
  summarise(total_in = sum(usd))
in_money <- left_join(names_df, in_money) %>% mutate(total_in = ifelse(is.na(total_in), 0, total_in))

# Get total income paid to any one person which should have been collective BY YEAR
in_money_year <- income %>%
  group_by(name = paid_to, year) %>%
  summarise(total_in = sum(usd))
in_money_year <- left_join(left, in_money_year) %>% mutate(total_in = ifelse(is.na(total_in), 0, total_in))

# Get total income paid to any one person which should have been collective pre/post LLC
in_money_llc <- income %>%
  group_by(name = paid_to, llc) %>%
  summarise(total_in = sum(usd))
in_money_llc <- left_join(left_llc, in_money_llc) %>% mutate(total_in = ifelse(is.na(total_in), 0, total_in))

# Get wages paid and not yet reimbursed
out_wages <- wages_paid %>%
  group_by(name) %>%
  summarise(wages_paid = sum(usd))
out_wages <- left_join(names_df, out_wages) %>% mutate(wages_paid = ifelse(is.na(wages_paid), 0, wages_paid))

# Get wages paid and not yet reimbursed BY YEAR
out_wages_year <- wages_paid %>%
  group_by(name, year) %>%
  summarise(wages_paid = sum(usd))
out_wages_year <- left_join(left, out_wages_year) %>% mutate(wages_paid = ifelse(is.na(wages_paid), 0, wages_paid))

# Get wages paid and not yet reimbursed by pre/post llc
out_wages_llc <- wages_paid %>%
  group_by(name, llc) %>%
  summarise(wages_paid = sum(usd))
out_wages_llc <- left_join(left_llc, out_wages_llc) %>% mutate(wages_paid = ifelse(is.na(wages_paid), 0, wages_paid))

# Join all together
together <- left_join(hours_money, ex_money) %>% left_join(in_money) %>% left_join(out_wages)

# Join all together BY YEAR
together_year <- left_join(hours_money_year, ex_money_year) %>% left_join(in_money_year) %>% left_join(out_wages_year)

# Join all together BY pre/post llc
together_llc <- left_join(hours_money_llc, ex_money_llc) %>% left_join(in_money_llc) %>% left_join(out_wages_llc)


# Round all columns
together <- together %>%
  mutate(total_hours = round(total_hours, digits = 2),
         total_ex = round(total_ex, digits = 2),
         total_in = round(total_in, digits = 2),
         wages_paid = round(wages_paid, digits = 2)) %>%
  rename(expenditures_absorbed = total_ex,
         income_absorbed = total_in)

# Round all columns BY YEAR
together_year <- together_year %>%
  mutate(total_hours = round(total_hours, digits = 2),
         total_ex = round(total_ex, digits = 2),
         total_in = round(total_in, digits = 2),
         wages_paid = round(wages_paid, digits = 2)) %>%
  rename(expenditures_absorbed = total_ex,
         income_absorbed = total_in)

# Round all columns BY pre/post llc
together_llc <- together_llc %>%
  mutate(total_hours = round(total_hours, digits = 2),
         total_ex = round(total_ex, digits = 2),
         total_in = round(total_in, digits = 2),
         wages_paid = round(wages_paid, digits = 2)) %>%
  rename(expenditures_absorbed = total_ex,
         income_absorbed = total_in)

# Convert hours to usd
x <- together
wage <- params$hourly_rate
new_wage <- params$new_hourly_rate
client_wage <- params$client_hourly_rate
new_client_wage <- params$new_client_hourly_rate
x <- x %>%
  mutate(wages_earned = 
           (total_hours_client_new * new_client_wage) +
           (total_hours_client_old * client_wage) +
           (total_hours_internal_new * new_wage) +
           (total_hours_internal_old * wage))

# Convert hours to usd PER YEAR
x_year <- together_year
x_year <- x_year %>%
  mutate(wages_earned = 
           (total_hours_client_new * new_client_wage) +
           (total_hours_client_old * client_wage) +
           (total_hours_internal_new * new_wage) +
           (total_hours_internal_old * wage))

# Convert hours to usd by pre/post llc
x_llc <- together_llc
x_llc <- x_llc %>%
  mutate(wages_earned = 
           (total_hours_client_new * new_client_wage) +
           (total_hours_client_old * client_wage) +
           (total_hours_internal_new * new_wage) +
           (total_hours_internal_old * wage))



# Calculate current balance
together_reactive <-  x %>%
  mutate(balance = wages_earned - wages_paid + expenditures_absorbed - income_absorbed)

together_reactive_year <-  x_year %>%
  mutate(balance = wages_earned - wages_paid + expenditures_absorbed - income_absorbed)

together_reactive_llc <-  x_llc %>%
  mutate(balance = wages_earned - wages_paid + expenditures_absorbed - income_absorbed)
```

### Overall balance (ie, balance after wages)

<large>
<strong>

```{r, results = 'asis'}
bank_val <- round(dplyr::last(bank$usd), digits = 2)
x <- together_reactive
x <- x %>%
  summarise(balance = sum(balance)) %>%
  mutate(balance_numeric = balance) %>%
  mutate(balance = paste0(balance, ifelse(balance > 0, ' in the red', ' in the black')))  %>%
  mutate(balance_bank = balance_numeric - bank_val) %>%
  mutate(balance_bank_text = paste0(abs(balance_bank), ifelse(balance_bank > 0, ' in the red', ' in the black')))

cat(paste0('Paying wages and reimbursing expenses will make us ', x$balance, '.'))
cat(paste0('But, we have ', bank_val, ' USD in the bank.'))
cat(paste0('So, if we pay all wages and expense reimbursements, we will end up ', x$balance_bank_text, '.'))
```

</large>
</strong>


## Hours worked over time 

### Overall cumulative

The below chart shows the cumulative number of hours worked for DataBrew over time.

```{r}
x <- hours %>%
  group_by(date, name) %>%
  summarise(hours = sum(total_hours)) %>%
  ungroup 
left <- expand.grid(date = seq(min(x$date),
                               max(x$date),
                               by = 1),
                    name = sort(unique(x$name)))
joined <- left_join(left, x)
x <- joined %>%
  mutate(hours = ifelse(is.na(hours), 0, hours)) %>%
  arrange(date) %>%
  group_by(name) %>%
  mutate(cum_hours = cumsum(hours)) %>%
  ungroup

maximum <- x %>% filter(date == max(date))

library(ggrepel)
cols <- colorRampPalette(RColorBrewer::brewer.pal(n = 8, 'Spectral'))(length(unique(x$name)))
ggplot(data = x,
       aes(x = date,
           y = cum_hours,
           color = name)) +
  geom_line(alpha = 1, size = 1) +
  theme_fivethirtyeight() +
  labs(x = 'Date',
       y = 'Cumulative hours',
       title = 'Hours worked',
       subtitle = 'Not including "non-shared" hours (ie, Xing\'s work for YouthRex)') +
  scale_color_manual(name = '',
                     values = cols) +
  geom_text_repel(data = maximum,
                  aes(x = date,
                      y = cum_hours,
                      color = name,
                      label = cum_hours)) 
```

### By month

The below shows the number of hours worked by calendar month.

```{r}
pd <- x %>%
  group_by(date = as.Date(cut(date, 'month')),
           name) %>%
  summarise(hours = sum(hours)) %>%
  ungroup

ggplot(data = pd,
       aes(x = date,
           y = hours)) +
  geom_bar(stat = 'identity') +
  facet_wrap(~name) +
  theme_fivethirtyeight() +
  geom_text(aes(label = hours),
            nudge_y = 15, 
            alpha = 0.5,
            size = 2)
```

```{r, eval = FALSE}
DT::datatable(x)
```

### How much employees are owed

The below shows how much employees are owed in order to "cash out"

```{r}
x <- together_reactive
x$cad <- round(x$balance * currency$usd_to_cad[currency$date == max(currency$date)], digits = 2)

ggplot(data = x,
       aes(x = name,
           y = balance)) +
  geom_bar(stat = 'identity',
           fill = 'darkblue',
           alpha = 0.6) +
  geom_label(aes(label = paste0(round(balance, digits = 2), ' USD\nor\n',
                                round(cad, digits = 2), ' CAD')),
             size = 3,
             y = 5000) +
  theme_fivethirtyeight() +
  labs(x = 'Who',
       y = 'USD',
       title = 'Amount owed to workers',
       subtitle = 'Wages worked plus expenses incurred minus amounts previously paid out') 
# DT::datatable(together_reactive)
databrew::prettify(together_reactive)
```

## How to pay employees

Payments for wages should be kept separate from payments for expenses. The below shows how these should be carried out.

```{r}
z <- x %>%
  dplyr::select(name, wages_earned, wages_paid, expenditures_absorbed, income_absorbed) %>%
  group_by(name) %>%
  summarise(wages_owed = wages_earned - wages_paid - income_absorbed,
            reimbursements_owed = expenditures_absorbed) %>%
  mutate(`Total` = wages_owed + reimbursements_owed)
canadify <- function(x){
  round(x * currency$usd_to_cad[currency$date == max(currency$date)], digits = 2)
}
z <- data.frame(z)
for(j in 2:ncol(z)){
  z[,j] <- paste0(round(z[,j], digits = 2), ' (', canadify(z[,j]), ' CAD)')
}
# z <- z %>% filter(! name %in% c('Wengsi', 'Coloma'))
databrew::prettify(z)

```


# Year-specific totals

The below shows totals, _per year_. Values are USD (in parenthesis: CAD). Note that values are only included within the period date range (`r params$start_date` through `r params$end_date`). Also note that the following spouses are absorbed into their partner's totals: Coloma (Joe), Xing (Ben):


```{r}
show <- together_reactive_year %>%
  mutate(amount_paid = wages_paid + income_absorbed) %>%
  mutate(amount_earned_wages = wages_earned) %>%
  mutate(amount_earned_reimbursements = expenditures_absorbed) %>%
  dplyr::select(name, year, amount_paid, amount_earned_wages, amount_earned_reimbursements) %>%
  # Adjust amounts paid based on amounts already paid out
  mutate(paid_less_than_expenses = amount_paid < amount_earned_reimbursements) %>%
  mutate(amount_paid_reimbursements = ifelse(paid_less_than_expenses, amount_paid, amount_earned_reimbursements)) %>%
  mutate(amount_paid_wages = amount_paid - amount_paid_reimbursements) %>%
  mutate(owed = amount_earned_wages + amount_earned_reimbursements - amount_paid_wages - amount_paid_reimbursements) %>%
  dplyr::select(-paid_less_than_expenses) %>%
  mutate(owed_wages = amount_earned_wages - amount_paid_wages) %>%
  mutate(owed_reimbursements = amount_earned_reimbursements - amount_paid_reimbursements) %>%
  dplyr::select(Year = year,
                Name = name,
              `Earned (wages)` = amount_earned_wages,
              `Earned (reimbursements)` = amount_earned_reimbursements,
                Paid = amount_paid,
                `Paid (wages)` = amount_paid_wages,
                `Paid (reimbursements)` = amount_paid_reimbursements,
               `Owed` = owed,
                `Owed (wages)` = owed_wages,
                `Owed (reimbursements)` = owed_reimbursements)
 

# Total row
total_row <- show %>%
  group_by(Name) %>%
  summarise_all(funs(sum)) %>%
  ungroup %>%
  mutate(Year = 'Total')

# Combine
show <- bind_rows(show %>% mutate(Year = as.character(Year)), total_row) %>%
  dplyr::arrange(Name)
show_names <- names(show)
z <- show
z <- data.frame(z)
for(j in c(3:ncol(z))){
  z[,j] <- paste0(round(z[,j], digits = 2), ' (', canadify(z[,j]), ' CAD)')
}
names(z) <- show_names
show <- z

databrew::prettify(show, nrows = nrow(show))
```



# Pre-post LLC totals

The below shows totals, broken down by the period pre LLC (prior to Feb 25 2019) and the period post LLC (Feb 25 2019 and beyond). Values are USD (in parenthesis: CAD). Note that values are only included within the period date range (`r params$start_date` through `r params$end_date`):



```{r}
show <- together_reactive_llc %>%
  mutate(amount_paid = wages_paid + income_absorbed) %>%
  mutate(amount_earned_wages = wages_earned) %>%
  mutate(amount_earned_reimbursements = expenditures_absorbed) %>%
  dplyr::select(name, llc, amount_paid, amount_earned_wages, amount_earned_reimbursements) %>%
  # Adjust amounts paid based on amounts already paid out
  mutate(paid_less_than_expenses = amount_paid < amount_earned_reimbursements) %>%
  mutate(amount_paid_reimbursements = ifelse(paid_less_than_expenses, amount_paid, amount_earned_reimbursements)) %>%
  mutate(amount_paid_wages = amount_paid - amount_paid_reimbursements) %>%
  mutate(owed = amount_earned_wages + amount_earned_reimbursements - amount_paid_wages - amount_paid_reimbursements) %>%
  dplyr::select(-paid_less_than_expenses) %>%
  mutate(owed_wages = amount_earned_wages - amount_paid_wages) %>%
  mutate(owed_reimbursements = amount_earned_reimbursements - amount_paid_reimbursements) %>%
  dplyr::select(LLC = llc,
                Name = name,
              `Earned (wages)` = amount_earned_wages,
              `Earned (reimbursements)` = amount_earned_reimbursements,
                Paid = amount_paid,
                `Paid (wages)` = amount_paid_wages,
                `Paid (reimbursements)` = amount_paid_reimbursements,
              `Owed` = owed,
                `Owed (wages)` = owed_wages,
                `Owed (reimbursements)` = owed_reimbursements)
 

# Total row
total_row <- show %>%
  dplyr::select(-LLC) %>%
  group_by(Name) %>%
  summarise_all(funs(sum)) %>%
  ungroup %>%
  mutate(LLC = 'Total')

# Combine
show <- bind_rows(show, total_row) %>%
  dplyr::arrange(Name)
show_names <- names(show)
z <- show
z <- data.frame(z)
for(j in c(3:ncol(z))){
  z[,j] <- paste0(round(z[,j], digits = 2), ' (', canadify(z[,j]), ' CAD)')
}
names(z) <- show_names
show <- z

databrew::prettify(show, nrows = nrow(show))
```


```{r, results = 'asis'}
# cat(paste0('## Appendix: raw data '))
# 
# cat(paste0('### Expenses: raw data '))
# 
# DT::datatable(expenses)
# 
# cat(paste0('### Hours: raw data '))
# 
# DT::datatable(hours)
# 
# cat(paste0('### Income: raw data '))
# 
# DT::datatable(income)
```
